Verifying Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
Typos in index scheme definition.

\begin{definition}
  An \emph{index scheme} is a vector of size $n$ (an $n$-vector) with
  values drawn from $\domainVal = \mathbb{Z} \cup \{\infty\}$.  Values
  in $\mathbb{Z}$ represent the offsets of neighbourhood indices
  (\ie{}, the constant integer $c$ in an indexing expression of the
  form $i \pm c$, Def.~\ref{def:neighbour}) and $\infty$ is a wild-card
  representing both constant indices and un-specified indices. Throughout $u, v, w$ range over
  index schemes and $u_i$ denotes the $i^{th}$ element of $u$. We
  write $(\domainVal)^n$ for the set of all $n$-dimensional schemes.
\end{definition}

>>>>

\begin{definition}
  An \emph{index scheme} is a vector of size $n$ (an $n$-vector) with
  values drawn from $\domainVal = \mathbb{Z} \cup \{\infty\}$.  Values
  in $\mathbb{Z}$ represent the offsets of neighbourhood indices
  (\ie{}, the constant integer $c$ in an indexing expression of the
  form $i \pm c$, Def.~\ref{def:neighbour}) and $\infty$ is a wild-card
  representing both constant indices and unspecified indices. Throughout, $u, v,
  w$ range over
  index schemes and $u_i$ denotes the $i^{th}$ element of $u$. We
  write $(\domainVal)^n$ for the set of all $n$-dimensional schemes.
\end{definition}
